### 2021-05-10 yfcc100m/paper/vldb2021/design.tex
Minor update to design

VDMS implements the typical client-server architecture that handles
client queries transactionally and concurrently, similar to what most common
relational and non-relational database systems
\cite{mysql, postgresql, chang2008bigtable} use.
The main difference between other data management systems and VDMS is that
it goes beyond the typical supported data types (string, integers, floats,
blobs, JSON-documents, etc), recognizing visual entities (image, videos,
feature vectors, etc) as first class citizens.
VDMS API enable users to insert, index, process, and query visual data,
as well as provides full support for inserting, indexing and querying
user-defined metadata.
Users interact with both metadata and visual data using a unified API,
in a transactional manner.

>>>>

VDMS implements the typical client-server architecture that handles
client queries transactionally and concurrently, similar to what most common
relational and non-relational database systems
\cite{mysql, postgresql, chang2008bigtable} use.
The main difference between other data management systems and VDMS is that
it goes beyond the typical supported data types (string, integers, floats,
blobs, JSON-documents, etc.), recognizing visual entities (image, videos,
feature vectors, etc.) as first class citizens.
VDMS API enable users to insert, index, process, and query visual data,
as well as provides full support for inserting, indexing and querying
user-defined metadata.
Users interact with both metadata and visual data using a unified API,
in a transactional manner.
